Nonlinear Spatio-Temporal Modelling using the Integro-Difference Equation

### 2010-07-17 ltx/second_order_framework/second_order_manuscript.tex

%to delete
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{yellow}{#1}}}}}

@@

\section{Introduction}
\begin{enumerate}
	\item General background and motivation
	\item Aims and hypotheses
	\item Specific background
	\item Point out specific things we are doing and why they are important
	\item Paper layout
\end{enumerate}

@@

\section{Second order stochastic Neural Field Model}

>>>>

\usepackage{anysize} 									%<-use this for checking equation length
\marginsize {1.7cm}{1.5cm}{1cm}{1cm} 				%<-use this for checking equation length

%to delete
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}

@@

\section{Introduction}
\dean{Hi Parham: I have added some headings. Hope they are ok. I was going to cut and paste the derivation in, but I thought I would let you do it, because it goes back and forth a little. When we get a structure (doesn't have to be how I laid it out) it will be easier for me to work on it too.}
\begin{enumerate}
	\item General background and motivation
	\item Aims and hypotheses
	\item Specific background
	\item Point out specific things we are doing and why they are important
	\item Paper layout
\end{enumerate}

\section{Method}
\subsection{Derivation of the Integro-Difference Equation Neural Field Model}

\subsection{Model-Reduction: Derivation of Finite Dimensional State-Space Model}

\subsection{Frequency Analysis: Determining Basis Function Width and Spacing}
Need something about the method of placement of basis functions and sampling of the field. \dean{Are we going to go for a triangular grid of basis functions?}

\subsection{Determining Connectivity Kernel Width}

\subsection{Estimation: Expectation Maximization Algorithm}

\section{Results}

\subsection{Frequency Analysis}
Confirmation of field sampling by sensors and show spatial frequency constraints on the approximated field.

\subsection{Connectivity Kernel Width}

\subsection{State and Parameters Estimation}
Need to show the parameter distributions

\section{Discussion and Conclusion}

@@

\section{Second-Order Stochastic Neural Field Model}
